### 2012-12-05 inst/examples/policycosts/writeup.Rmd
writeup generates plots for fishstock now as well as harvest

```{r p1, dependson="tidy", fig.width=12}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
```

@@

```{r Figure4}
frac_lost <- seq(0.1,0.9, length=5)
out <- lapply(frac_lost, pdgControl:::fig4, ls())
out <- melt(out)
colnames(out) = c("statistic", "penalty", "value", "index")
out <- cbind(out[1:3], fraction__npv_lost = frac_lost[out$index])
Figure4 <- ggplot(out) + geom_point(aes(fraction_npv_lost, value, col=penalty)) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic, scales="free_y")
Figure4
````

>>>>

```{r p1, dependson="tidy", fig.width=12}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
```

@@

# Figure 4

```{r helperfn1}
fig4 <- function(fraction_lost){
closest <- function(x, v){
  which.min(abs(v-x))
}
dt_npv <- data.table(fees)
index <- dt_npv[,closest(fraction_lost, (npv0-value)/npv0), by=variable]
apples_index <- index$V1
names(apples_index) = index$variable
apples <- c2[index$V1]
names(apples) = index$variable
L2_policy <- policies$L2[[apples_index["L2"]]]$D
L1_policy <- policies$L1[[apples_index["L1"]]]$D
fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
quad_policy <- policies$quad[[apples_index["quad"]]]$D

quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
sims <- lapply(1:50, function(reps) list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"])),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"])),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_increase_policy, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            quad_policy, z_g, z_m, z_i, 
                            opt$D, profit=quad_profit, penalty= none)
  ))

  #Make data tidy (melt), fast (data.tables), and nicely labeled.
  dat <- melt(sims, id=names(sims[[1]][[1]]))  
  dt <- data.table(dat)
  setnames(dt, "L1", "reps") # names are nice
  setnames(dt, "L2", "penalty_fn") # names are nice

  dt
}
```

```{r} 
# Helper functions to extract the summary stats in different variables
stats_harvest <- function(dt){
v <- dt[,var(harvest), by=c("penalty_fn", "reps")]
acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]
df <- cbind(v, acor$V1)
setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
df
}

stats_fishstock <- function(dt){
v <- dt[,var(fishstock), by=c("penalty_fn", "reps")]
acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]
df <- cbind(v, acor$V1)
setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
df
}
```

```{r helper2}
#' a simple function for reorganizing the data over the different "faction-lost" levels
get_trends <- function(tmp2){
  out <- melt(tmp2, id=c("reps", "var", "acor"))
  colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
  out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
  out <- data.table(out)
  Ev = out[,mean(var),by=c('penalty', 'fraction')]
  SDv = out[,sd(var),by=c('penalty', 'fraction')]
  Ea = out[,mean(acor),by=c('penalty', 'fraction')]
  SDa = out[,sd(acor),by=c('penalty', 'fraction')]
  harvest_trends <- data.table(penalty = Ev$penalty, 
                               fraction = Ev$fraction, 
                               Ev = Ev$V1, Ea = Ea$V1, 
                               SDv=SDv$V1, SDa = SDa$V1)
}
```

```{r Figure4}
frac_lost <- seq(0,1, length=20)
sims_at_each_apple <- lapply(frac_lost, fig4)
harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
havest_trends <- get_trends(harvest_stats)

Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

Fig4b <- ggplot(harvest_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
Fig4a
Fig4b
````

```{r}
fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
fishstock_trends <- get_trends(fishstock_stats)

FigS4a <- ggplot(fishstock_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

FigS4b <- ggplot(fishstock_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
FigS4a
FigS4b
```
